The Anatomy of a Hit: Statistically Learning from the Best

### 2024-04-18 paper/paper.qmd
updated paper
Simulated dataset, scraped artist data from billboard.

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the most impactful elements of the most successful musicians."
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/valence-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

@@

Throughout the history of the music industry, musicians successful or not have always pined for one thing - writing a hit and making it big. However, for large music firms, taking on musicians that have yet to generate considerable popularity is an large risk, since they are often gambling on an unknown je ne sais quoi, and often, any given artist is more likely to not produce a hit than produce a hit; this is easily shown through the presence of a few small "superstars" that consistently dominate the music market [@rosen1981]. This poses an interesting question for artists vying to become that superstar: what does make a song a "hit"?

@@

---

---

>>>>

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the most impactful elements of the most popular musicians."
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/popularity-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

@@

Throughout the history of the music industry, musicians successful or not have always pined for one thing - writing their first hit and making it big. However, for large music firms, taking on musicians that have yet to generate considerable popularity is a large risk, since they are often gambling on an unknown je ne sais quoi, and often, any given artist is more likely to not produce a hit than produce a hit; this is easily shown through the presence of a few small "superstars" that consistently dominate the music market [@rosen1981]. This poses an interesting question for artists vying to become that superstar: what does make a song a "hit"?

@@
